\speculake: Hiding Malware in Speculative Execution

### 2018-12-10 paper/introduction.tex
add blog citation

\speculake provides a new technique to malware authors, allowing them to hide
program functionality in code that appears to not execute at runtime. This technique
defeats existing static and dynamic analysis, making it especially difficult for
malware analysts to determine what a binary will do.

>>>>

\speculake provides a new technique to malware authors, allowing them to hide
program functionality in code that appears to not execute at runtime by
leveraging Spectre as a feature~\cite{necessaryBlog}. This technique defeats
existing static and dynamic analysis, making it especially difficult for malware
analysts to determine what a binary will do.
